Article 2:	Information-Seeking Behavior Decision-Making between Online Search and Interpersonal Networks: The Case of Covid-19 Vaccinations 

### 2022-01-24 paper2.Rmd
change chi2 to phi coefficient

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, 
               modelsummary, showtext, thematic, kableExtra, scales)

@@

# Abstract 
How do individuals perform information search, and what factors help them decide
which information search vehicle to utilize, such as interpersonal networks or
online tools, I investigate the above question  using individual survey data of
934 Adults in the United States and find that

Knowing that Google
trends data only encompasses a small portion of the information-seeking done by
modern humans, it is important to investigate what leads individuals to search
for a question online using a search engine versus more traditional means of
information gathering, such as network activation (asking someone in their
social network for informational support). I predict that few people will
activate their social network for informational support in my chosen case of
Covid-19 vaccinations because of the social cost of doing so and that the
majority will have utilized an online search engine.

@@

## section B: Research Questions
* How do computer-mediated or interpersonal network information-seeking strategies vary across populations? 
* What factors lead people to perform health information search online versus among social network ties? 
* How does the utilization of social networks, search engines, and social media as vary in the case of searching for information on the Covid-19 vaccine?

@@

My analytic strategy proceeds in four steps. In Tables \@ref(tab:table-1-desc) 
& \@ref(tab:table-2-desc), I present descriptive statistics for all study 
variables, including variable ranges, means, and standard deviations. For this 
paper, I rely heavily on logistic regression, modeled in `r`; specifically, I 
fit a series of Binomial Generalized Linear Models [@venables2002a]. In Table \@ref(tab:table-model-1)^[All tables in this paper were created with the modelsummary package in `r` [@modelsummary] ]
, I fit a logistic regression model predicting
whether someone sought information about Covid-19 using their sources of
information ('Received info') as well as various demographic variables such as
age, education level and race. Figure \@ref(fig:plot-model-1) then illustrates
the relationship between the coefficients and information seeking.^[Figures in this paper were all created using the `r` packages jtools [@jtools] and ggplot2 [@wickham_etal; @wickham11] ].
In Table \@ref(tab:table-model-2), I disaggregate information seeking behaviors
by investigating the difference in proportions of each of the vehicles in 
\@ref(tab:model-2-chi2) and then by modelling a series of logistic regressions 
that predict the 5 different avenues of seeking information about Covid-19: 
from another person, from a doctor, on an online forum, on a social networking 
site, or using an online search tool.
Finally, in Table \@ref(tab:table-model-3), I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook.  Figure \@ref(fig:plot-model-3) then illustrates
the relationship between the coefficients and vaccination outlook.

@@

## Information Search Vehicles
```{r model-2-chi2}
#| results = "asis"

chi <- rain %>% 
  select(pers = int_sought_fr_pers,
         dr = int_sought_fr_dr,
         forum = int_sought_fr_onlgroup,
         net = int_sought_fr_onlnet,
         search = int_sought_fr_onlsearch)

find_p <- function(x, y){
  tab <- table(x, y)
  as.numeric(chisq.test(tab)["p.value"])
}

chi_squared_tests <- 
tribble(~col, ~Person, ~Dr, ~`Online Forum`, ~`Online Network`, ~`Online Search`,
'Person',   NA, find_p(chi$pers, chi$dr), find_p(chi$pers, chi$forum), find_p(chi$pers, chi$net), find_p(chi$pers, chi$search),
'Dr',     NA, NA, find_p(chi$dr, chi$forum), find_p(chi$dr, chi$net), find_p(chi$dr, chi$search),
'Online Forum',  NA, NA, NA, find_p(chi$forum, chi$net), find_p(chi$forum, chi$search),
'Online Network',    NA, NA,NA, NA, find_p(chi$net, chi$search),
'Online Search', NA, NA, NA, NA, NA)

chi_squared_tests %>%
  mutate(across(where(is.numeric), ~ sprintf("%.3f", round(., digits = 3)))) %>% 
  mutate(Person = cell_spec(Person, format = "html", bold = Person < 0.05),
       Dr = cell_spec(Dr, format = "html", bold = Dr < 0.05),
       `Online Forum` = cell_spec(`Online Forum`, format = "html", bold = `Online Forum` < 0.05),
       `Online Network` = cell_spec(`Online Network`, format = "html", bold = `Online Network` < 0.05),
       `Online Search` = cell_spec(`Online Search`, format = "html", bold = `Online Search` < 0.05)) %>% 
  kable(., escape = FALSE,
      digits=3,  
      caption = "Pearson's $\\chi^2$ test with Yates' continuity
	correction  between each Information Search Vehicle",
      col.names = c("",'Person', 'Dr', 'Online Forum', 'Online Network', 'Online Search')      ) %>% 
  kable_styling(latex_options = c("hold_position", "striped"),
                full_width = F) %>%
  column_spec(column = 1, bold = T) %>% 
  footnote(c("Bolded values are significant using $\\alpha = 0.05$, two-tailed test"))
```

@@

To further investigate how people search for information, I asked those who had
sought information out intentionally, "How did you look for information about
the Covid-19 vaccine?" Results are displayed in Table \@ref(tab:table-model-2).
Because respondents could select as many responses as applicable, each response
is recorded as a dichotomous variable and modeling using logistic regression.
Modeling each response as a separate formula is useful for interpretation, but
there are important caveats: because each logistic regression is on a different
scale, one must not compare the magnitude of coefficients between models. We
can, however, use the direction and significance of the coefficients to draw
conclusions about these different forms of information search vehicles.

TODO interpret table \@ref(tab:model-2-chi2), the chi2 tests to see differences

The first model predicts whether or not a respondent sought information
intentionally about Covid-19 vaccinations by asking their doctor or another
health professional. First and foremost, I find that those who received
information about Covid-19 vaccinations were 
`r round(exp(part2_models$Doctor$coefficients[['receive_i_fr_dr1']]), 2)` times
more likely to seek out more information from their doctor than those who had 
not ( _p_ < 0.001). However, receiving information from other vehicles also 
increased the odds of seeking out information from medical professions. Those who
received information from a person like a friend or a relative were 
`r round(exp(part2_models$Doctor$coefficients[['receive_i_fr_pers1']]), 2)` times
more likely to ask their doctor ( _p_ < 0.001), while those who received 
information from the news or television were
`r round(exp(part2_models$Doctor$coefficients[['receive_i_fr_tv1']]), 2)`
times more likely ( _p_ < 0.01). I also find that those who received information
from an online forum like a subreddit were 
`r label_percent()(round(exp(part2_models$Doctor$coefficients[['receive_i_fr_onlgroup1']]), 2)-1)`
more likely to ask their doctors than those who hadn't ( _p_ < 0.05). Finally, 
respondents with an associate's degree or higher were 
`r label_percent()(round(exp(part2_models$Doctor$coefficients[['college1']]), 2)-1)`
more likely to ask their doctor for information on the Covid-19 vaccinations
than those who held less education ( _p_ < 0.01).

>>>>

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, psych,
               modelsummary, showtext, thematic, kableExtra, scales)

@@

# Abstract 
How do individuals perform information search, and what factors help them decide
which information search vehicle to utilize, such as interpersonal networks or
online tools, I investigate the above question using individual survey data of
934 Adults in the United States and find that X and Y. Furthermore, this paper
demonstrates that searching for a question online using a search engine or
social network was more common than traditional means of information gathering,
such as network activation (asking someone in their social network for
informational support). Using X and Y theory I predict that that few people will
activate their social network for informational support in my chosen case of
Covid-19 vaccinations because of the social cost of doing so but fail to find
evidence for this thesis. I also investigate which information channels are
associated with vaccinations against the virus, and find that social netwokring
sites are associated with lower rates. I also find important ethnocracial
differences in information search vehicles utilization and vaccination
reception.

<!-- TODO this needs a lot of work but its a start -->

@@

Research Questions

* How do computer-mediated or interpersonal network information-seeking strategies vary across populations? 
* What factors lead people to perform health information search online versus among social network ties? 
* How does the utilization of social networks, search engines, and social media as vary in the case of searching for information on the Covid-19 vaccine?

@@

My analytic strategy proceeds in four steps. In Tables \@ref(tab:table-1-desc) 
& \@ref(tab:table-2-desc), I present descriptive statistics for all study 
variables, including variable ranges, means, and standard deviations. For this 
paper, I rely heavily on logistic regression, modeled in `r`; specifically, I 
fit a series of Binomial Generalized Linear Models [@venables2002a]. In Table \@ref(tab:table-model-1)^[All tables in this paper were created with the modelsummary package in `r` [@modelsummary] ]
, I fit a logistic regression model predicting
whether someone sought information about Covid-19 using their sources of
information ('Received info') as well as various demographic variables such as
age, education level and race. Figure \@ref(fig:plot-model-1) then illustrates
the relationship between the coefficients and information seeking.^[Figures in 
this paper were all created using the `r` packages jtools [@jtools] and ggplot2 [@wickham_etal; @wickham11] ].
In Table \@ref(tab:model-2-phi) I disaggregate information seeking behaviors by
investigating the difference in proportions of each of the 5 different avenues
of seeking information about Covid-19: from another person, from a doctor, on an
online forum, on a social networking site, or using an online search tool. I
investigate these differences through a phi coefficient [@warrens08], otherwise
known as a mean square contingency coefficient which is used to investigate the
degree of association between two binary variables. ^[To calculate the Phi
Coefficient, I utilize the Psych `r` package [@psych] ] I then investiage the
associations between my predictors and the 5 information search vehicles by
modelling a series of logistic regressions in Table \@ref(tab:table-model-2).
Finally, in Table \@ref(tab:table-model-3), I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook.  Figure \@ref(fig:plot-model-3) then
illustrates the relationship between the coefficients and vaccination outlook.

@@

## Information Search Vehicles

```{r model-2-phi}
phi <- rain %>% 
  select(pers = int_sought_fr_pers,
         dr = int_sought_fr_dr,
         forum = int_sought_fr_onlgroup,
         net = int_sought_fr_onlnet,
         search = int_sought_fr_onlsearch)

find_phi <- function(x, y){
  tab <- table(x, y)
  phi(tab, digits = 3)
}

phi_squared_tests <- 
  tribble(~col, ~Person, ~Dr, ~`Online Forum`, ~`Social Networking Site`, ~`Online Search`,
          'Person',   NA_complex_, find_phi(phi$pers, phi$dr), find_phi(phi$pers, phi$forum), find_phi(phi$pers, phi$net), find_phi(phi$pers, phi$search),
          'Dr',     NA, NA, find_phi(phi$dr, phi$forum), find_phi(phi$dr, phi$net), find_phi(phi$dr, phi$search),
          'Online Forum',  NA, NA, NA, find_phi(phi$forum, phi$net), find_phi(phi$forum, phi$search),
          'Social Networking Site',    NA, NA,NA, NA, find_phi(phi$net, phi$search),
          'Online Search', NA, NA, NA, NA, NA)

kable(phi_squared_tests, digits=3,  
      caption = "Phi Coefficient ($\\phi$) of binary association between each Information Search Vehicle",
      col.names = c("",'Person', 'Dr', 'Online Forum', 'Social Networking Site', 'Online Search')) %>% 
  kable_styling(latex_options = c("hold_position", "striped"),
                full_width = F)

@@

To further investigate how people search for information, I asked those who had
sought information out intentionally, "How did you look for information about
the Covid-19 vaccine?" Because respondents could select as many responses as
applicable, each response is recorded as a dichotomous variable. I first
investigate how each Information Search Vehicle are related to each other using
the Phi Coefficient ($\\phi$) of binary association between each Information
Search Vehicle pair. The Phi coefficient can be interpreted like a correlation
coefficient, with numbers closer to -1 or positive one indicating a very strong
relationship [@warrens08]. Table \@ref(tab:model-2-chi2) shows the results of
these coefficients. Out of the five information search vehicles investigated,
there is evidence that the vehicles are distinctly different concepts because
most coefficients fall under 0.3, the general rule of thumb for correlation 
coefficients to indicate a relationship. There does seem to be a relationship
between Online Forums and Social Networking Sites, possibly due to an
individual's propensity to use online networks over in-person networks. These
coefficients indicate a weak relationship between any two vehicles of
information search and and that respondents in my sample utilize each of these a
little bit differently.

Results of each logistic regression are displayed in Table \@ref(tab:table-model-2).
Modeling each response as a separate formula is useful for interpretation, but
there are important caveats: because each logistic regression is on a different
scale, one must not compare the magnitude of coefficients between models. We
can, however, use the direction and significance of the coefficients to draw
conclusions about these different forms of information search vehicles.

The first model in Table \@ref(tab:table-model-2) predicts whether or not a
respondent sought information intentionally about Covid-19 vaccinations by
asking their doctor or another health professional. First and foremost, I find
that those who received information about Covid-19 vaccinations were
`r round(exp(part2_models$Doctor$coefficients[['receive_i_fr_dr1']]), 2)` times
more likely to seek out more information from their doctor than those who had 
not ( _p_ < 0.001). However, receiving information from other vehicles also 
increased the odds of seeking out information from medical professions. Those who
received information from a person like a friend or a relative were 
`r round(exp(part2_models$Doctor$coefficients[['receive_i_fr_pers1']]), 2)` times
more likely to ask their doctor ( _p_ < 0.001), while those who received 
information from the news or television were
`r round(exp(part2_models$Doctor$coefficients[['receive_i_fr_tv1']]), 2)`
times more likely ( _p_ < 0.01). I also find that those who received information
from an online forum like a subreddit were 
`r label_percent()(round(exp(part2_models$Doctor$coefficients[['receive_i_fr_onlgroup1']]), 2)-1)`
more likely to ask their doctors than those who hadn't ( _p_ < 0.05). Finally, 
respondents with an associate's degree or higher were 
`r label_percent()(round(exp(part2_models$Doctor$coefficients[['college1']]), 2)-1)`
more likely to ask their doctor for information on the Covid-19 vaccinations
than those who held less education ( _p_ < 0.01).
